Methodology for Assessing the State of the Practice for Domain X

### 2020-10-11 StateOfPractice/Methodology/Methodology.tex
fixed typos in Methodology document

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
The candidate software can be found through search engine queries targeting authoritative lists of software from the domain, such as lists on GitHub and swMATH, and through searching domain related publications. Domain experts are also asked for their suggestions and are asked to review the list. The candidate software should have the following properties:

>>>>

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
The candidate software can be found through search engine queries targeting authoritative lists of software from the domain, such as lists on GitHub and swMATH, and by searching domain related publications. Domain experts are also asked for their suggestions and are asked to review the list. The candidate software should have the following properties:
